\section{Approve exam slots submission}

\begin{description}
	\item[Business Event Description] \ 
		\par The scheduling committee received a message (i.e. submission) containing
		the preferred exam slots of a student and now needs to check of this
		configuration of exam slots is allowed.
	\item[Business Use Case Name] \ 
		\par Approve exam slots submission
	\item[Triggering business event] \ 
		\par The scheduling committee receives a submission of the preferred exam
		slots of a student.
	\item[Preconditions] \
	\begin{itemize}
		\item The scheduling committee has received the submission of the preferred
		exam slots of a student.
	\end{itemize}
	\item[Active stakeholders] \ 
	\begin{itemize}
		\item Scheduling committee: checks the preferred exam slots submission of the
		student.
	\end{itemize}
	\item[Interested stakeholders] \ 
		\begin{itemize}
		\item Student: wants that his preferred exam slots submission is approved.
		\end{itemize}
	\item[Normal business flow] \ 
	\begin{enumerate}
	  	% 1
	  	\item The scheduling committee checks that no chosen slots overlap.
	  	% 2
	  	\item The scheduling committee checks that no chosen slots are overbooked.
	  	% 3
	  	\item The scheduling committee notices that all checks succeed.
	  	% 4
	  	\item The scheduling committee sends an approval message to the student.
	  	% 5
	  	\item The student receives the approval message and is now allowed to take
	  	the exams on the chosen slots.
	\end{enumerate}
	\item[Alternative business flow] \ 
		\par None
	\item[Exception business flow] \ 
	\begin{description}
		\item[3a] if the scheduling committee notices that some checks have failed
		then, 
		\begin{enumerate}
		  \item The scheduling committee sends a disapproval message to the student.
		  \item The student receives the disapproval message and has to change his
		  chosen exam slots to a valid configuration.
		\end{enumerate}
	\end{description}
	\item[Outcome (postcondition)] \ 
		\par The student is allowed to take his exams on the chosen exam slots and is
		notified of this fact by the scheduling committee.
\end{description}