\section{Approve tolerance}

\begin{description}
	\item[Business Event Description] \ 
		\par 
	\item[Business Use Case Name] \ 
		\par Approve tolerance
	\item[Triggering business event] \ 
		\par The toleration committee has received a request for a toleration of a
		certain course from a certain student. The committee, however, has to check that the
		request can be granted. 
	\item[Preconditions] \
	\begin{itemize}
		\item The toleration committee has received the tolerance form.
	\end{itemize}
	\item[Active stakeholders] \ 
	\begin{itemize}
		\item Toleration committee: checks to see if the tolerance can be granted
	\end{itemize}
	\item[Interested stakeholders] \ 
		\begin{itemize}
		\item Student: wants to know if his request is accepted
		\item Educational committee: can incorporate any tolerances in approving study
		contracts.
		\end{itemize}
	\item[Normal business flow] \ 
	\begin{enumerate}
	  	% 1
	  	\item The toleration committee glances through the form. 
	  	% 2
	  	\item The toleration committee checks that the student has enough tolerance
	  	budget for the toleration.
	  	% 3
	  	\item The toleration committee tolerates the shortcoming.
	  	% 6
	  	\item The tolerance committee sends an approval message to the student and
	  	notifies the educational committee of this tolerance.
	  	% 7
	  	\item The student receives the approval message and is now granted a
	  	tolerance for the chosen course.
	\end{enumerate}
	\item[Alternative business flow] \ 
		\par None
	\item[Exception business flow] \ 
	\begin{description}
		\item[2a] if the tolerance committee comes out negative (e.g. because of a
		lack of tolerance budget) then,
		\begin{enumerate}
		  \item The tolerance committee sends a disapproval message to the student.
		  \item The student receives the disapproval message and is not granted the
		  chosen tolerance.
		\end{enumerate}
	\end{description}
	\item[Outcome (postcondition)] \ 
		\par Both the student and the educational committee know about the acceptance
		of the tolerance request.
\end{description}
