\section{Choose exam slots}

\begin{description}
	\item[Business Event Description] \ 
		\par After choosing his preferred courses, the student decides to choose an
		exam slot for each of these courses.
	\item[Business Use Case Name] \ 
		\par Choose exam slots
	\item[Triggering business event] \ 
		\par The student wants to choose his exam slots for his preferred courses.
	\item[Preconditions] \
	\begin{itemize}
		\item The student has made the selection of the courses he wants to take.
	\end{itemize}
	\item[Active stakeholders] \ 
	\begin{itemize}
		\item Student: wants to choose when he does each exam of each chosen course
	\end{itemize}
	\item[Interested stakeholders] \ 
		\begin{itemize}
		\item Lector(s): wants to know when he has to interrogate which student about
		the courses he teaches.
		\end{itemize}
	\item[Normal business flow] \ 
	\begin{enumerate}
	  	% 1
	  	\item The student takes the form for choosing exam slots.
	  	% 2
	  	\item The student provides the necessary identifying information (found on
	  	his student card).
	  	% 3
	  	\item The student chooses an exam slot for each course.
	  	% 4
	  	\item The student sends the form to the scheduling committee.
	  	% 5
	  	\item The scheduling committee checks the form and approves the chosen exam
	  	slots, \textbf{include} \emph{(UC11: Approve Exam Slots Submission)}.
	\end{enumerate}
	\item[Alternative business flow] \
		\par None 
	\item[Exception business flow] \ 
		\par None
	\item[Outcome (postcondition)] \ 
		\par The chosen exam slots are approved by the scheduling committee and the
		student is notified of this fact.
\end{description}