\section{Choose courses}

\begin{description}
	\item[Business Event Description] \ 
		\par The student decides it's time to choose his courses that are part of his
		contract(s). At the beginning of a study year the student chooses his courses
		for the whole year, at the beginning of the second semester the student can
		choose (and hence change) his courses for the second semester.
	\item[Business Use Case Name] \ 
		\par Choose courses
	\item[Triggering business event] \ 
		\par The student decides it's time to choose his courses that are part of his
		contract(s) and takes the necessary steps.
	\item[Preconditions] \
	\begin{itemize}
		\item The student is registered for at least 1 study contract.
	\end{itemize}
	\item[Active stakeholders] \ 
	\begin{itemize}
		\item Student: wants to choose his courses for the year or second semester.
		\item Educational Committee: supervises that the courses selected by the
		student are allowed to be taken by the student.
	\end{itemize}
	\item[Interested stakeholders] \ 
	\begin{itemize}
		\item Didactical team of the courses the student wants to follow.
	\end{itemize}
	\item[Normal business flow] \
	\begin{enumerate}
	  	% 1
	  	\item The student takes the form for choosing his courses.
	  	% 2
	  	\item The student provides the necessary identifying information (found on
	  	his student card). 
	  	% 3
	  	\item The student assigns for which study contract (for which he is
	  	registered) he wants to choose his courses.
	  	% 4
	  	\item The student chooses the courses.
	  	% 5
	  	\item The student sends the form to the educational committee.
	  	% 6
	  	\item The educational committee receives and checks the courses
	  	configuration and approves the configuration, \textbf{include} \emph{(UC5:
	  	Approve courses submission)}.
	\end{enumerate}
	\item[Alternative business flow] \
	\begin{description}
		\item[4a]If the student has more than 1 study contract he has to
		repeat the steps 1 - 4 of the basic flow for each study contract.
			\begin{enumerate} 
	  			\item The student sends all forms to the educational committee.
			\end{enumerate}
	\end{description}
	\item[Exception business flow] \ 
	\par None
	\item[Outcome (postcondition)] \  
		\par The student is allowed to follow the chosen courses of his registered
		study contracts.
\end{description}
