\section{Register for study contract}

\begin{description}
	\item[Business Event Description] \ 
		\par The student wants to register for a diploma contract.
	\item[Business Use Case Name] \ 
		\par Register for study contract
	\item[Triggering business event] \ 
		\par The student wants to register for a diploma contract and decides to take the necessary steps.
	\item[Preconditions] \ 
	\begin{itemize}
		\item The student has to be a registered student at Wellington University and
		hence has a student card.
	\end{itemize}
	\item[Active stakeholders] \ 
	\begin{itemize}
		\item Student: wants to be registered for a diploma contract.
		\item Study contract committee: controls the approval or disapproval of the
		contract the student wishes to obtain.
	\end{itemize}
	\item[Interested stakeholders] \ 
		\begin{itemize}
		\item University board: interested in new students, contract determines the
		inscription fee.
		\item Faculties: interested in new students that follow a study contract supervised
		by them
		\end{itemize}
	\item[Normal business flow] \ 
	\begin{enumerate}
	  	% 1
	  	\item The student takes the form for starting a new study contract.
	  	% 2
	  	\item The student fills in the required identification information by using
	  	his student card (with on it his unique student number).
	  	% 3
	  	\item The student chooses to register for a diploma contract.
	  	% 4
	  	\item The student chooses the bachelor or master contract of his choice.
	  	% 5
	  	\item The student sends the form to the study contract committee.
	  	% 6
	  	\item The study contract committee receives and approves the form,
	  	\textbf{include} \emph{(UC3: Approve study contract)}.
	\end{enumerate}
	\item[Alternative business flow] \ 
	\begin{description}
		\item[3a] Instead of a diploma contract the student chooses to register for a
		credit contract. 
		\begin{enumerate}
		  \item Resume at step 5 of the basic flow.
		\end{enumerate}
		\item[3b] Instead of a diploma contract the student chooses to register for an
		exam contract. 
		\begin{enumerate}
		  \item Resume at step 5 of the basic flow.
		\end{enumerate}
	\end{description}
	\item[Exception business flow] \ 
	\begin{description}
		\item[6a] If the check of the study contract committee comes out negative
		(e.g. he wants to follow a master study while he still has to follow a
		full bachelor year), then 
		\begin{enumerate}	
		  \item The student can't follow the chosen diploma contract.	
		  \item The study contract committee sends a disapproval message to the
		  student.
		  \item The student receives the disapproval message, and is not allowed to
		  follow the chosen diploma contract.
		  \item The student can try to register for another diploma contract by
		  returning to step 1 in the normal flow.
		\end{enumerate}
	\end{description}
	\item[Outcome (postcondition)] \
		\par The student now follows the chosen study contract. The faculty who
		supervises that contract is aware that a new student has signed up.
\end{description}
