\section{Choose course}

\par \emph{As a registered student, I can choose a course for a study contract.}

\subsection{Path}

\begin{enumerate}
  \item The system gives the registered student an overview of the study
  contracts he has.
  \item The student selects a study contract for which he wants to choose a
  course.
  \item The system gives the registered student an overview of the courses he
  can choose.
  \item The registered student selects a course of the overview and thereby
  chooses to follow it.
  \item The registered student deselects 0 or more courses of the overview and
  thereby chooses to not follow it.
  \item The system registers the student's choice(s) to display them on the next
  visit.
  \item The system confirms the new choices via sending an email to the
  registered student. 
\end{enumerate}

\subsection{Confirmation}

\begin{description}
\item[Test 1:] Verify that the registered student can only see his study
contracts.
\item[Test 2:] Verify that the registered student can only see the courses he
can follow according to his study contract(s).
\item[Test 3:] Verify that the registered student can choose a single course.
\item[Test 4:] Verify that the registered student can choose multiple courses at
a time.
\item[Test 5:] Verify that the registered student can choose to deselect a
course.
\item[Test 6:] Verify that the registered student can choose to deselect
multiple courses.
\item[Test 7:] Verify that the registered student receives a confirmation email
within 15 minutes after selection.
\end{description}
