\section{Approve courses submission}

\begin{description}
	\item[Name] \
		\par Approve courses submission
	\item[Short description] \ 
			\par The educational committee has received a submission of a chosen courses
			configuration and needs to check if it can be approved. If so, it has to
			approve it and notify the student.
	\item[Trigger] \ 
			\par The educational committee has received a submission of a chosen courses
			configuration which it now has to check (i.e. look if it is a valid submission).
	\item[Primary actor(s)] \ 
		\begin{itemize}
		  \item Educational Committee: checks the received submission.
		\end{itemize}
	\item[Secondary actor(s)] \ 
		\begin{itemize}
		  \item Student: wants to see the submission of his courses configuration as
		  approved by the educational committee.
		\end{itemize} 
	\item[Preconditions] \ 
	\begin{itemize}
		\item The educational committee has received the submission of the student.
		\item Each employee of the educational committee (that is active in the use
		case) is logged in as a educational committee employee.
	\end{itemize}
	\item[Normal flow] \ 
	\begin{enumerate}
	  	% 1
	  	\item The educational committee navigates to the page where it finds all the
	  	information of the student (i.e. passed courses, study contracts, personal
	  	information, \ldots).
	  	% 2
	  	\item The educational committee uses this information to perform a series of
	  	checks:
	  	\begin{enumerate}
	  	  \item The educational committee checks if the student meets the entry
	  	  requirements for each submitted course.
	  	  \item The educational committee checks that if the student is a full time
	  	  student, the total number of study points is at least 40 and doesn't
	  	  exceed 75, and that if the student is a part-time student, the total
	  	  number of study points is a number between 0 and 30 (inclusive).
	  	  \item The educational committee checks that if the student is a first year
	  	  student, he has chosen all the courses of the first phase.
	  	\end{enumerate}
	  	% 3
	  	\item The educational committee concludes that all the tests are passed.
	  	% 4
	  	\item The educational committee indicates that the configuration is
	  	approved.
	  	\item The system registers this and sends an approval message to the
	  	student.
	  	% 5
	  	\item The student receives the approval message and is now fully accepted
	  	for a study program.
	\end{enumerate}
	\item[Alternative flow] \
		\par None
	\item[Postcondition(s)] \ 
	\begin{itemize}
		\item The educational committee has approved the submitted courses
		configuration and this information is registered in the system.
		\item The student has been notified of this fact.
	\end{itemize}
	\item[Exception(s)] \ 
	\begin{description}
		\item[3a] The educational committee concludes that 1 or more checks come out
		negative.
		\begin{enumerate}
			\item The educational committee sends a disapproval message to the student.
			\item The student receives the disapproval message and needs to change his
			courses configuration if he wants to see his configuration approved.
		\end{enumerate}
	\end{description}
\end{description}
