\section{Choose Courses}

\begin{description}
	\item[Name] \
		\par Choose Courses
	\item[Short description] \ 
			\par The student chooses the courses for his student contract(s) to finalize
			his study program. It's the next logical step after having registered for a
			study contract.
	\item[Trigger] \ 
			\par The student decides to choose his courses for his registered study
			contract(s) and takes the necessary steps.
	\item[Primary actor(s)] \ 
		\begin{itemize}
		  \item Student: wants to select courses for his study contract(s).
		\end{itemize}
	\item[Secondary actor(s)] \ 
		\begin{itemize}
		  \item Didactical team: interested in students who will follow a course they
		  are part of.
		\end{itemize} 
	\item[Preconditions] \ 
	\begin{itemize}
		\item The student is registered for one or more study contracts.
		\item The student is logged in and is on his personal page.
	\end{itemize}
	\item[Normal flow] \ 
	\begin{enumerate}
	  	% 1
	  	\item The student navigates to the choose courses section of his personal
	  	page.
	  	% 2
	  	\item The system displays the choose courses page for the student.
	  	% 3
	  	\item The student selects the study contract for which he wants to choose
	  	the courses.
	  	% 4
	  	\item The system shows the selected courses configuration that the student
	  	saved on an earlier visit to the page.
	  	% 5
	  	\item The student searches for the courses he wants.
	  	% 6
	  	\item The student selects the courses he wants to follow.
	  	% 7
	  	\item The student deselects 0 or more courses that he doesn't want to
	  	follow anymore in the configuration.
	  	% 8
	  	\item The student saves his chosen courses configuration
	  	% 9
	  	\item The system records this chosen courses configuration to show to the
	  	student on his next visit on the page.
	  	% 10
	  	\item The system makes exam slots available to the student for the newly
	  	selected courses and disables those of unselected ones.
	  	% 11
	  	\item If the student wants, he can choose the exam slots of the chosen
	  	courses at this point, \textbf{extend} \emph{(UC6: Choose Exam Slots)}.
	  	% 12
	  	\item If the student decides that his global course configuration (i.e. the
	  	total course configuration for each of his study contracts) is final, he
	  	can submit this configuration directly, \textbf{extend} \emph{(UC5: Submit
	  	Course Configuration)}.
	\end{enumerate}
	\item[Alternative flow] \
		\begin{description}
		\item[4a] The system doesn't display a previously saved courses
		configuration since the student never visited the choose courses page for the
		chosen study contract before.
			\begin{enumerate}
			  \item Resume the basic flow at step 5.
			\end{enumerate}
		\end{description}
	\item[Postcondition(s)] \ 
		\par The student has made a new chosen courses configuration of one of his 
		study contracts and this configuration is saved to the system.
	\item[Exception(s)] \ 
		\par None
\end{description}