\section{Choose exam slots}

\begin{description}
	\item[Name] \
		\par Choose exam slot
	\item[Short description] \ 
			\par The student wants to register for an exam slot of a course he intends to
			follow.
	\item[Trigger] \ 
			\par The student decides to register for an exam slot in order to complete
			one or more study programs.
	\item[Primary actor(s)] \ 
		\begin{itemize}
		  \item Student: wants to book an exam slot for a course.
		\end{itemize}
	\item[Secondary actor(s)] \ 
		\begin{itemize}
		  \item Lector(s): wants to know when which students are doing an exam for
		  a course he is teaching.
		\end{itemize}
	\item[Preconditions] \ 
	\begin{itemize}
		\item The student has chosen the courses he wants to select an exam
		slot for.
	\end{itemize}
	\item[Normal flow] \ 
	\begin{enumerate}
	  	% 1
	  	\item The student navigates to the exam slot selection page.
	  	% 2
	  	\item The system displays the exam slot selection page.
	  	% 3
	  	\item The student overviews the different possibilities and selects the most
	  	appropriate one.
	  	% 4
	  	\item The system registers the student's choice and blocks that slot for
	  	reservations of other students.
	  	% 5
	  	\item The system notifies the lectors teaching the course where the exam
	  	slot belongs that there is a new booking.
	\end{enumerate}
	\item[Alternative flow] \
		\begin{description}
			\item[4a] The student had already selected an exam slot for that course (and
			he wants to select another one because it suits him better for some reason).
			\begin{enumerate} 
			  \item The system allows new bookings for the previously reserved slot.
			  \item The system registers the student's choice and blocks
			  that slot for other reservations.
			  \item The system notifies the lectors teaching the course where the exam
			  slot belongs that there is a new booking.
			\end{enumerate}
		\end{description}
	\item[Postcondition(s)] \
	\begin{description} 
		 \item The exam slot is booked for the student (no other students can book
		 this slot anymore). 
		 \item The student now has that exam slot as exam moment for the
		corresponding course. 
		\item Any previously booked slot is now reopened.
	\item[Exception(s)] \ 
		\par None
\end{description}