\section{Register New Student}

\begin{description}
	\item[Name] \
		\par Register New Student
	\item[Short description] \ 
			\par A student wants to register himself to be a student at Wellington
			University. To obtain such a inscription he goes to the student
			administration building during the inscription days.
	\item[Trigger] \ 
			\par The student goes to the student administration building of Wellington
			University to inscribe himself as a Wellington student.
	\item[Primary actor(s)] \ 
		\begin{itemize}
		  \item Student: wants to be a registered Wellington student.
		  \item Registration committee: checks the student information and enters it
		  into the system.
		\end{itemize}
	\item[Secondary actor(s)] \ 
		\par None
	\item[Preconditions] \ 
	\begin{itemize}
		\item The student has arrived at the desk for new registrations in the student administration building
		\item The student has brought the required documents and information:
		diploma's, evidence for passing matriculations, register number, passport
		picture, personal information (telephone number, address, cellphone number,
		\ldots).
		\item The student is not yet registered at Wellington University.
		\item The registration committee is logged in.
	\end{itemize}
	\item[Normal flow] \ 
	\begin{enumerate}
	  	% 1
	  	\item The student hands over the required documents to the people of the
	  	registration committee behind the desk.
	  	% 2
	  	\item The registration committee checks if the handed over information is
	  	complete.
	  	% 3
	  	\item The registration committee navigates to the corresponding student-	  
	  	registration page.
	  	% 4
	  	\item The system displays the student-registration page.
	  	% 5
	  	\item The registration committee enters all the required information into
	  	the system.
	  	% 6
	  	\item The registration committee submits that information to the system
	  	making the student a registered student of Wellington Univerisity.
	  	% 7
	  	\item The system returns the unique student number.
	  	% 8
	  	\item The system demands the student to hand in a password. 
	  	% 9
	  	\item The student hands in a password.
	  	% 10
	  	\item The registration committee uses the unique student number to make a
	  	student card for the student.
	  	% 11
	  	\item The registration committee hands over the student card to the student.
	  	% 12
	  	\item The student accepts all these documents.
	  	% 13
	  	\item The student leaves the student administration building.
	\end{enumerate}
	\item[Alternative flow] \
		\par None
	\item[Postcondition(s)] \ 
	\begin{itemize}
		\item The student is a registered student at Wellington University
	\end{itemize}
	\item[Exception(s)] \ 
		\begin{description}
			\item[9a] The password was less than 6 characters.
			\begin{enumerate}
			  \item The system displays an error and invites the student to try again
			  \item Return to step 8 in the normal flow.
			\end{enumerate}
		\end{description}
			
\end{description}
