\section{Submit course configuration}

\begin{description}
	\item[Name] \
		\par Submit course configuration
	\item[Short description] \ 
			\par The student decides that his global course configuration (i.e. the total
			course configuration for each of his study contracts) is final and wants to
			submit this global configuration as a next step to become fully inscribed for
			a study program. 
	\item[Trigger] \ 
			\par The student wants to make his chosen courses configurations final.
	\item[Primary actor(s)] \ 
		\begin{itemize}
		  \item Student: wants to finalize his chosen courses configurations.
		\end{itemize}
	\item[Secondary actor(s)] \ 
		\begin{itemize}
		  \item Educational committee: receives the submission of chosen courses.
		\end{itemize} 
	\item[Preconditions] \ 
	\begin{itemize}
		\item The student is logged in.
		\item The student has chosen an exam slot for each chosen course (that has an
		exam).
	\end{itemize}
	\item[Normal flow] \ 
	\begin{enumerate}
	  	% 1
	  	\item The student navigates to the courses submission page.
	  	% 2
	  	\item The system displays the courses submission page.
	  	% 3
	  	\item The student selects to submit his saved courses configurations.
	  	% 4
	  	\item The system displays a warning that the submission is final.
	  	% 5
	  	\item The student selects to continue.
	  	% 6
	  	\item The system sends a message containing the course configuration and
	  	some additional information (name of the student and his studentnumber) to
	  	the educational committee.
	  	% 7
	  	\item The educational committee receives that message.
	  	% 8
	  	\item The educational committee checks the configuration and approves it,
	  	\textbf{include} \emph{(UC8: Approve Courses Submission)}.
	\end{enumerate}
	\item[Alternative flow] \
		\par None
	\item[Postcondition(s)] \ 
		\par The courses configurations are submitted and approved.
	\item[Exception(s)] \ 
		\par None
	\item[Remarks] \
		\par This use case is an extension of UC4: Choose courses.
\end{description}